---
output: 
  pdf_document:
    latex_engine: pdflatex
    template: svm-latex-cv.tex
geometry: margin=1in

title: "CV"
author: Shawn Graham

jobtitle: "Associate Professor of Digital Humanities"
address: "Department of History · Carleton University · Ottawa, Ontario"

email: shawn.graham@carleton.ca
# github: shawngraham
phone: "x2842"
web: electricarchaeology.ca
updated: no

keywords: R Markdown, academic CV, template

fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 11pt
linkcolor: blue
urlcolor: blue


---

# Education

*University of Reading*, Ph.D., Archaeology \hfill 2002

*University of Reading*, M.A., City of Rome \hfill 1998

*Wilfrid Laurier University*, B.A. Hons, Archaeology \hfill 1997

# Employment

*Carleton University, Department of History*

Associate Professor \hfill 2014-2017

Assistant Professor \hfill 2010-2014

# Professional Honours

# Current Research Interests

# Publications

##Books

```{r echo=FALSE, results="asis",comment=FALSE}
library(RefManageR)
file_books <- ReadBib("books.bib")
dates <- unlist(unique(file_books$year))[order(unlist(unique(file_books$year)),decreasing = TRUE)]
#Prints recerences
for (date in dates) {
  print(file_books[list(year=date)],.opts = list(style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n")
}

```


## Chapters in Edited Books

```{r echo=FALSE, results="asis",comment=FALSE}

file_journals <- ReadBib("chapters.bib")
dates <- unlist(unique(file_journals$year))[order(unlist(unique(file_journals$year)),decreasing = TRUE)]

for (date in dates) {
  
  print(file_journals[list(year=date)],.opts = list(style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n")
}
```

## Articles in Refereed Journals

```{r echo=FALSE, results="asis",comment=FALSE}

file_journals <- ReadBib("articles.bib")
dates <- unlist(unique(file_journals$year))[order(unlist(unique(file_journals$year)),decreasing = TRUE)]

for (date in dates) {
  
  print(file_journals[list(year=date)],.opts = list(style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n")
}
```

## Articles in Refereed Edited Collections

```{r echo=FALSE, results="asis",comment=FALSE}

file_journals <- ReadBib("ref-art-ed-coll.bib")
dates <- unlist(unique(file_journals$year))[order(unlist(unique(file_journals$year)),decreasing = TRUE)]

for (date in dates) {
  
  print(file_journals[list(year=date)],.opts = list(style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n")
}
```

## Articles in Refereed Conference Proceedings

## Major Encyclopedia or Dictionary Articles

## Catalogues

```{r echo=FALSE, results="asis",comment=FALSE}

file_journals <- ReadBib("catalogues.bib")
dates <- unlist(unique(file_journals$year))[order(unlist(unique(file_journals$year)),decreasing = TRUE)]

for (date in dates) {
  
  print(file_journals[list(year=date)],.opts = list(style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n")
}
```

## Textbooks

## Published Technical Reports

## Creative Writing

## Articles in Non-Refereed Journals and Miscellaneous Scholarly Publications

```{r echo=FALSE, results="asis",comment=FALSE}

file_journals <- ReadBib("non-reviewed-articles.bib")
dates <- unlist(unique(file_journals$year))[order(unlist(unique(file_journals$year)),decreasing = TRUE)]

for (date in dates) {
  
  print(file_journals[list(year=date)],.opts = list(style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n")
}
```

## Book Reviews

```{r echo=FALSE, results="asis",comment=FALSE}

file_journals <- ReadBib("reviews.bib")
dates <- unlist(unique(file_journals$year))[order(unlist(unique(file_journals$year)),decreasing = TRUE)]

for (date in dates) {
  
  print(file_journals[list(year=date)],.opts = list(style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n")
}
```

# Editorial Responsibilities

# Papers Presented
## ...to learned societies

```{r echo=FALSE, results="asis",comment=FALSE}
file_conf <- ReadBib("presentation-learned.bib")
dates <- unlist(unique(file_conf$year))[order(unlist(unique(file_conf$year)),decreasing = TRUE)]

#Prints recerences
for (date in dates) {
  print(file_conf[list(year=date)],.opts = list(style="markdown",bib.style ="authoryear" ,max.names =10,dashed=FALSE))
  cat("\n")
}
```

## ...to other academic bodies

## ...non-academic talks

# Other Important Forms of Scholarly Impact

# Research Income and Grants

```{r echo=FALSE}
grants <- read.csv("grants.csv")
```

This following section provides a summary of research income to date which totals `r paste0("$",format(sum(grants$Amount), big.mark=","))`, with `r paste0("$",format(sum(grants[grants$PI_CO_I == "PI",]$Amount), big.mark=","))` as Principal Investigator (PI) and `r paste0("$",format(sum(grants[grants$PI_CO_I == "Co-A",]$Amount), big.mark=","))` as Co-Applicant (Co-A) and `r paste0("$",format(sum(grants[grants$PI_CO_I == "Collaborator",]$Amount), big.mark=","))` as Collaborator.


```{r echo=FALSE, results="asis",comment=FALSE}

years <- unique(grants$Year)[order(unique(grants$Year),decreasing = TRUE)] #Get year list

for (year in years){#years

  cat("*",year,"\n")
  
  tmp_grant <- grants[grants$Year == year,]
  
for (i in 1:nrow(tmp_grant)){#line printing loop
  cat(paste0("\t"))
  cat("+",paste0("_",tmp_grant[i,]$Funder,"_")," ",paste0(tmp_grant[i,]$Title),paste0("(",tmp_grant[i,]$PI_CO_I,")"),paste0("**$",format(sum(tmp_grant[i,]$Amount), big.mark=",")),"**","\n")
  
}#line print

}#years

```

# Service to the Profession

# Consultancies and Contract Research

# Academic Responsibilities

## Graduate Courses Taught

## Undergraduate Courses Taught

## Supervision 

### Ph.D

### M.A.

### Honours
### Theses examined for other departments at Carleton

# Administrative Responsibilities at Carleton

## Department

## Faculty

## University